Bulk Semantic Annotation with an Partially Known Knowledge Base

### 2024-11-13 doc/cicm25-sysdesc/sysdesc.tex
draining

@@

In an earlier attempt to support semantic annotation in IDEs, we tried named-entity
recognition (NER) for classification of ``likely annotation candidate words''
\cite{hutterer:msc23}, however this classification was not precise enough in the
distinction in ``technical terms'' and ordinary english noun phrases and named entities --
the relevant task for annotation, and so made it impractical, especially, since it could
not enter the actual annotations and import directives automatically. But maybe using the
NER-based approach, after the \srf annotation process might change the tradeoffs
involved. In any case, the overall workflow suggested by the NER-based approach --
especially after the verbalizations covered by the existing content commons\ednote{better
  to speak of the domain model here?} -- is geared towards adding to the content commons.

This is complementary to the \srf approach,

>>>>

\section{Practical Evaluation}

The step-through

@@

In an earlier attempt to support semantic annotation in IDEs, we tried named-entity
recognition (NER) for classification of ``likely annotation candidate words''
\cite{hutterer:msc23}, however this classification was not precise enough in the
distinction in ``technical terms'' and ordinary english noun phrases and named entities --
the relevant task for annotation, and so made it impractical, especially, since it could
not enter the actual annotations and import directives automatically. But maybe using the
NER-based approach, after the \srf annotation process might change the tradeoffs
involved. In any case, the overall workflow suggested by the NER-based approach --
especially after the verbalizations covered by the existing domain model\ednote{introduce
  in the definition above that the domain model is all definitions, not only in the
  smglom?} -- is geared towards adding modules and symbols -- the ones discovered by NER
-- to the domain model.
